MLH1 Results Outline

### 2020-02-27 doc/Results.rmd
missed the bus

log.SC.male.poly_musc <- glm(Rec.group ~ mean_SC, 
              data=Male.poly.Mouse.Table_BivData_4MM[Male.poly.Mouse.Table_BivData_4MM$subsp == "Musc",],  family=binomial(link="logit"))

@@

```{r Q2.SClength.ttest, echo=FALSE, include=FALSE}
#COMPARISONS ACROSS ALL CLASSES

>>>>

#log.SC.male.poly_musc <- glm(Rec.group ~ mean_SC, 
#              data=Male.poly.Mouse.Table_BivData_4MM[Male.poly.Mouse.Table_BivData_4MM$subsp == "Musc",],  family=binomial(link="logit"))

@@

```{r Q2.SClength.ttest, echo=FALSE, include=FALSE, eval=FALSE}
#COMPARISONS ACROSS ALL CLASSES
